\begin{soln}
\begin{claim}
$L_1$ is not context-free
\end{claim}
\begin{proof}
Suppose $L_1$ is context-free. Then it must satisfy the pumping lemma for context-free languages.
But as we will show in the claim below $L_1$ does not satisfy the pumping lemma. Hence $L_1$ can
not be context-free.
\begin{claim}
For all $p \in \mathbb{N}$ there exists a string $w \in L_1$ such that $|w| \geq p$ and
for all strings $u, v, x, y, z \in \Sigma^*$ such that $w = uvxyz$  and one of the following does 
not hold
\begin{enumerate}
    \item  $|vy| > 0$
    \item $|vxy| \leq p$
    \item  $uv^ixy^iz \in L_1$ for all $i \in \mathbb{N} \cup \{0\}$.
\end{enumerate}
\end{claim}
\begin{proof}
For any $p \in \mathbb{N}$ consider the string $w = a^p b^p c^p d^p$ and its partition $w = uvxyz$.
Then we have 3 cases
\begin{enumerate}
    \item $vxy$ is a substring of $a^p b^p$. In this case if we assume property 1 and 2 then by pumping once (i.e. $i=2$)
    we have that $uv^2xy^2z \notin L_1$ because number of a's increase while number of c's remain the same.
    Hence property 3 is violated here.
    
    \item $vxy$ is a substring of $b^p c^p$. In this case if we assume property 1 and 2 then by pumping once (i.e. $i=2$)
    we have that $uv^2xy^2z \notin L_1$ because number of b's increase while number of d's remain the same.
    Hence property 3 is again violated here.
     
    \item $vxy$ is a substring of $c^p d^p$. In this case if we assume property 1 and 2 then by pumping once (i.e. $i=2$)
    we have that $uv^2xy^2z \notin L_1$ because number of c's increase while number of a's remain the same.
    Hence property 3 is again violated here.
\end{enumerate}
Thus for each case we have proved the claim.
\end{proof}
Hence $L_1$ can not be context-free.
\end{proof}

\begin{claim}
$L_2$ is context-free
\end{claim}
\begin{proof}
Consider the language of grammar of $G = (N, \Sigma, R, S)$ where $N = \{S, S'\}$,
and $\Sigma = \{a, b, c, d\}$ and following rules under $R$:
\begin{align*}
    S &\rightarrow \varepsilon\\
    S &\rightarrow a S d\\
    S &\rightarrow S'\\
    S' &\rightarrow \varepsilon\\
    S' &\rightarrow b S' c\\
\end{align*}

\begin{claim}
$L_2 \subseteq \mathcal{L}(G)$
\end{claim}
\begin{proof}
Consider any string $s \in L_2$ as $a^m b^n c^n d^m$.
Then to generate this string via grammar $G$ we may apply the production rule 2 $m$ times,
followed by production rule 3 and then production rule 5 applied $n$ times finally followed by production rule 4.
In the corner case when $m, n = 0$ we may simply apply production rule 1 and be done with it.
\end{proof}

\begin{claim}
$\mathcal{L}(G) \subseteq L_2$
\end{claim}
\begin{proof}
\begin{claim}
If $S' \derives s$ then $s = b^n c^n$ for some $n \in \mathbb{N} \cup \{0\}$
\end{claim}
\begin{proof}
Proof by induction on number of production rules used in shortest derivation.
\paragraph{Base Case} Number of production rules used = 1, then we have must have used the rule 4 giving us $s = \varepsilon$.
\paragraph{Inductive Case} If we have used more than one production rule then our first production rule must have been
$S' \produces b S' c \derives b b^n c^n c$ where the derivation follows from inductive hypothesis.
\end{proof}

\begin{claim}
If $S \derives s$ then $s = a^m b^n c^n d^m$ for some $m, n \in \mathbb{N} \cup \{0\}$
\end{claim}
\begin{proof}
Proof by induction on number of production rules used in shortest derivation.
\paragraph{Base Case} Number of production rules used = 1, then we have must have used the rule 1 giving us $s = \varepsilon$.
\paragraph{Inductive Case} If we have used more than one production rule then our first production rule must have been either
\begin{enumerate}
    \item  $S \produces a S d \derives a a^m b^n c^n d^m d$ where the derivation follows from inductive hypothesis.
    \item $S \produces S' \derives b^n c^n$ where the derivation follows from the previous claim. Here $m = 0$.
\end{enumerate}
\end{proof}
\end{proof}

\end{proof}
\end{soln}